---
title: "R Course Day2"
author: "R. Rosenast"
date: "06.02.2018"
output: 
  html_notebook:
    toc: true
    toc_float: true
    number_sections: true
---

Notebooks are a combinatoin of Literate programming, dynamic document and reproducible research.
* Can be used to showcase the project. Its understandable and can execute parts of code.
* Integration of other languages, e.g. SQL and Python.
* REPL -> Read Evaluate Print Loop
* 

# R Markdown Header 1: MARKDOWN
## R Markdown Header 2: Different Markdown

* **BOLD**
* *italics*
* ~~scratched Text~~
* superscript ^2
* [a link](www.google.com)
* inline R Code: 6 minus 4 = `r 6-4` (back-tick + r + code + back-tick)

## Code Chunks
plots and tables:
```{r}
plot(cars)
```

echo=FALSE
```{r, echo=FALSE, warnings=FALSE}
plot(cars)
```


```{python}
print("cars")
```

## Latex
*easy to include LaTeX documentation in your report
Inline Latex
$A= \pi*r^2$

Block Equation
$$\sqrt{100}=10$$

# Shiny app
* Shiny is a platform for creating interactive R programs embedded into a webpage.
* Shiny is made by the folks at Rstudio.

## Traps
possible traps that might lead to wrong decisions:

1. Importance trap (Focus on relevant metrics!)
2. Context trap (Context implies on what to focus, e.g. absolute or relative figures.)
3. Causality trap (Is a relationship based on correlation or causation?)

## Setup
```{r, echo=FALSE}
# 1. Download and install the R package shiny
install.packages('shiny')
library('shiny')

# creating the user interface (HTML page)
ui <- fluidPage()

# running the app
server <- function(input, output){}
shinyApp(ui = ui, server = server)
```





